---
title: "Lsn34"
author: "Clark"
header-includes:
   - \usepackage{bbm}
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Admin


Say we are testing, generically $H_0: \theta = \theta_0$ vs $H_a: \theta> \theta_0$.  Our first step is determining what our test statistic is.  For large sample tests it may make sense to us:

\vspace{2.in}

When we use this as our test statistic it has a distribution of $Z \sim N(0,1)$.  From here we either fix or determine our rejection region so $P(Z > z)=\alpha$.  Note here we can also solve for our rejection region in terms of $\hat{\theta}$

\vspace{2.in}

As we previously discussed, the probability of commiting a Type II error is:

\vspace{2.in}

In order to find this we need to stipulate a value for $\theta_a > \theta_0$.  In terms of $k$ we are searching for:

$$P(\hat{\theta}\leq k| \theta=\theta_a)$$

Note, for $\hat{\theta}$ we still have the CLT, so if $\theta=\theta_a$ our $Z$ value is NOT $\frac{\hat{\theta}-\theta_0}{\sigma_{\hat{\theta}}}$ but rather since we are assuming $\theta=\theta_a$ we have:

$$Z_a = \frac{\hat{\theta}-\theta_a}{\sigma_{\hat{\theta}}}$$
Note the difference here.  So, the probability of commiting a Type II error is the probability that 

$$P(\hat{\theta}\leq k| \theta=\theta_a)$$
Or, $P(Z_a \leq \frac{k-\theta_a}{\sigma_{\hat{\theta}}})$

Again we have $Z_a \sim N(0,1)$ so the calculations can be performed straight forwardly.  

In Exercise 10.19 WMS state

The output voltage for an electric circuit is specified to be 130.  A sample of 40 independent readings on the voltage for this circuit gave a sample mean of 128.6 and standard deviation 2.1.  Test the hypothesis that the average coutput voltage is 130 against the alternative that it is less than 130.  Use a test with level .05.

First we define our test statistic

\vspace{2.in}

In R we could write

```{r}
Z<- (128.6-130)/(2.1/sqrt(40))
Z
RR<-qnorm(.05)   #Lower Tail test so .05 here
Z<RR
```

Now, we note that if the voltage falls as low as 128, serious consequences may result.  What is the probability of a type II error if $\mu=128$?.  Note here that 

```{r}
k<-2.1/sqrt(40)*RR+130
#In terms of Theta, our RR is 
cat(-Inf,k,sep=",")
```

So to find Power we need to find the probability that $\hat{\mu}$ is not in the Rejection if, indeed $\mu=128$.  If we are not in the rejection region than we have not observed $\hat{\mu}=129.4538$ or lower, so we need the probability $\hat{\mu} > 129.45$ given $\mu =128$, or in other words we need 

$$P\left(\frac{\hat{\mu}-128}{\frac{2.1}{\sqrt{40}}} > \frac{129.4538-128}{\frac{2.1}{\sqrt{40}}}\right)$$

Or, as we know the distribution of $\frac{\hat{\mu}-128}{\frac{2.1}{\sqrt{40}}}$ is $N(0,1)$ we want

```{r}
1-pnorm((129.4538-128)/(2.1/sqrt(40)))
```
So the probability of committing a Type II error is pretty low.  What if  we have serious consequences if the voltage falls below 129?  Then we would have:

```{r}
1-pnorm((129.4538-129)/(2.1/sqrt(40)))
```
Graphically what is going on is:

\vspace{3.in}

As we previously talked about, there's no such thing as a free lunch.  If you want a lower $\alpha$ you are going to get a higher $\beta$ (see picture above).  One way we can correct for this though is to change $n$.  If we change $n$ what happens to $Z$?

Graphically if we change $n$ we get:

\vspace{2.in}

So, if we want a fixed value of $\alpha$ and a fixed value of $\beta$ the one lever we have to pull is $n$.  

Recall that $\alpha$ is

\vspace{1.in}

And $\beta$ is

\vspace{1.in}

So if we fix $\mu_0$, $\mu_a$, $\alpha$ and $\beta$ we can solve for what our book calls $z_{\alpha}$ and $z_{\beta}$

\vspace{1.in}

So solving for $k$ yields

\vspace{1.in}

Letting these things be equal, we get a formula for $n$

$$n=\frac{(z_{\alpha}-z_{\beta})^2 \sigma^2}{(\mu_{\alpha}-\mu_0)^2}$$

Let's put all this together with exercises 10.42 and 10.43

1.)  Write out Null/Alternative

2.)  Find Test Statistic

3.)  Find Rejection Region if given $\alpha$

4.)  Determine Rejection Region in terms of $\hat{\theta}$, $k$

5.)  Find $\frac{k-\theta_a}{\sigma_{\hat{\theta}}}$

6.)  Calculate $\beta$

7.)  Find $z_{\alpha}$ \begin{verbatim}qnorm(1-alpha)\end{verbatim}

8.) Find $z_{\beta}$ \begin{verbatim}-qnorm(beta)\end{verbatim}